---
title: "R Markdown document for the Getting and Cleaning Data class project"
author: "Christopher Stewart"
date: "November 22, 2014"
output: html_document
---


# Description of data

This data is derived from training and test experiments on 30 volunteers perforiming 6 activities: WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING. The data include a 561-feature vector with time and frequency domain variables found in X_test.txt. y_test.txt contains labels for the aforementioned activities.

## Scripts and data preparation

To begin, download the data here: https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip. Unzip it and put in a directory along with run_analysis.R. Running this R script merges the training and the test sets, yielding a txt file with the mean values for subjects and activity levels. 







For the scripts used to get and clean this data to work, 


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
